Evaluation of dynamic resource allocation strategies for overlay Apache Spark clusters on HPC

### 2019-05-02 paper.tex

In this paper, we will analyse the effects of pilot scheduling strategies with an 
overlay Spark cluster. Our evaluation will be broken down into two parts: 1)
the overall added value of pilots, and 2), tolerance to failures. Part 1 will 
investigate the effect of queuing times on pilot applications. 
Here we present SPA, a pilot-scheduling library for launching Spark applications 
on HPC infrastructures. This library currently enables the launching of Spark applications
on Slurm-based clusters by dividing the total amount of resources required and requesting
multiple instances of subsets of the resources at a time. When a single 
instance is started, a Standalone Spark cluster is started. Built-in 
fault-tolerance of Spark masters and workers is leveraged, in addition 
to Driver fault tolerance for Scala-based applications. When nodes are 
lost due to walltime expiration, additional pilot nodes are launched 
until the driver completes. SPA facilitates the execution of large 
neuroimaging Spark applications on HPC systems.

>>>>

In this paper, we will analyse the effects of pilot scheduling strategies with an 
overlay Spark cluster. Our evaluation will be broken down into two parts: 1)
the added value of pilots, and 2), tolerance to failures. For determining the 
added value of pilots, we will investigate the effect of queuing times on 
pilot applications as compared to a batch requests. As much of the application's
tolerance to failures are features brought on by the overlay Spark cluster, in
Part 2 we will introduce failures that would be typical to pilot scheduling 
approaches (e.g. node failures due to walltime expiration). This part will be 
broken down into master failures, driver failures and checkpointing. As pilots 
may need to be replenished during execution, we will also consider the effects of 
job queues \todo{reword}.
